\sysfull

### 2017-08-12 paper/evaluation.tex
partial commit to eval

We also used an alternative setup where the MSP-TS430RGZ48C launchpad was used
for continuous power experiments. We used internal timer for measuring run
time. For harvested energy, we used WISP\,5.0~\cite{wisp5,wisp} hardware and
ThingMagic Astra-EX integrated RFID reader set at 30\,dBm transmission power.
We used EDB~\cite{edb} to measure run time. Applications were cross-compiled
using GCC and Clang, so that we can use LLVM for \sys compiler. Version 3.8.0
was used for both Clang and LLVM.

@@

We compare \sys against state-of-the-art task-based runtime Chain~\cite{chain}. We are not comparing \sys against DINO~\cite{dino} or Mementos~\cite{mementos} (Refer to Section~\ref{sec:background_consistency}), as (i) Chain is the only modular execution model available to which we can compare \sys, and (ii) Chain proved already its superiority over sequential model counterparts (i.e. DINO and Mementos)\footnote{We need to note that although another very relevant task-based runtime has been recently presented and referenced many times throughout this paper---Alpaca~\cite{alpaca} (written by the same group as Chain)---except the recently accepted manuscript we did not have the access to Alpaca's code during the preparation of this paper. Therefore Alpaca was excluded from the evaluation.}.

The applications that were used in the evaluation are: (i) \textbf{bc}: counts bits in byte pseudo-random string using varying algorithms. Each result is compared for correctness; (ii) \textbf{cem}: emulates an embedded temperature sensing engine: measurements are randomly generated and are compressed using a LZW algorithm for  fixed entry dictionary and fixed byte block; (iii) \textbf{cuckoo}: implements Cuckoo filter---the program first stores a sequence of pseudo-random numbers, then queries the filter to recover it; (iv) \textbf{rsa}: encrypts predefined string with a predefined key; (v) \textbf{ar} performs nearest neighbour classification using randomly generated sequence of three-axes accelerometer data. This set of benchmarks is the same as used in~\cite{chain,alpaca}. In addition to Chain benchmarks new applications were implemented: (vi) \textbf{sort}: selection sort algorithm, and (vii) \textbf{dft}: discreet Fourier transform. All applications are compared in Table~\ref{table:compiler_result} in terms of source lines of code against Chain.

@@

>>>>

For some experiments (noted below) we used an alternative setup where the
MSP-TS430RGZ48C launchpad was used for continuous power experiments. We used
internal timer for measuring run time. For harvested energy, we used
WISP\,5.0~\cite{wisp5,wisp} hardware and ThingMagic Astra-EX integrated RFID
reader set at 30\,dBm transmission power at 915\,MHz.  We used EDB~\cite{edb}
to measure run time. Applications were cross-compiled using GCC and Clang,
allowing us to use LLVM for the \sys compiler. We used version 3.8.0 of both
Clang and LLVM.

@@

We compare \sys against state-of-the-art task-based runtime Chain~\cite{chain}.
We do not compare \sys to other, earlier systems, such as DINO~\cite{dino} or
Mementos~\cite{mementos} (cf. Section~\ref{sec:background_consistency}), as
Chain is the only task-based execution model available to which we can compare
\sys.

We evaluated \sys using benchmarks from the literature~\cite{chain,alpaca} and
several new programs: (i) \textbf{bc}: counts bits in byte pseudo-random string
using several algorithms, and compares results for correctness; (ii)
\textbf{cem}, which emulates an embedded temperature sensing engine and in
which measurements are randomly generated and compressed using LZW with a fixed
entry dictionary and fixed byte block; (iii) \textbf{cuckoo}: which implements
a Bloom-filter-like Cuckoo filter that first hashes a sequence of pseudo-random
numbers, then queries the filter to recover the sequence; (iv) \textbf{rsa}:
which encrypts a fixed string with a stored key; (v) \textbf{ar}: which
performs nearest neighbour classification of randomly generated data modeling a
three-axis accelerometer.  This set of benchmarks overlaps with those used
in~\cite{chain,alpaca}. We implemented several new applications: (vi)
\textbf{sort}: selection sort algorithm on a fixed sequence of numbers, and
(vii) \textbf{dft}: discrete Fourier transform. All applications are compared
in columns eight and nine of Table~\ref{table:compiler_result} showing the
number of source lines of code compared to Chain.

@@

We evaluated \sys to show that it is easy to use and efficient across our
benchmarks.  We evaluate \sys's ease of use by characterizing \sys's automatic
task compiler.  We evaluate \sys efficiency by comparing its runtime
performance to Chain.  We characterize \sys by studying how its performance
varies due to coalescing and when using automatic task compilation versus
manual task compilation.
